---
title: "Customization Rank Test"
author: "Carl Pearson"
date: "2/27/2020"
output: html_document
---

Participants ranked what would be most important to them to customize. What options are significantly higher ranked than others?

```{r setup, echo=T, results='hide', message=F, warning=F}

#load packages
library(tidyverse)
library(rstatix)
library(ggpubr)
library(kableExtra)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 

#read data
dat <- read_csv("/Users/carlpearson/Documents/r_github/RHEL-Customization-Tickets/do_not_upload/cust_ranking_dat.csv",col_names = T)

#remove commas from colnames
colnames(dat) <- gsub(",",";", colnames(dat))
colnames(dat) <- gsub("-","", colnames(dat))

df_long <- dat %>% 
  rename(id=`Response ID`) %>% #rename variable
  mutate(id=as.numeric(as.factor(id))) %>% #anonymize data
  pivot_longer(-id) %>% #elongate data
  mutate(name_s=str_trunc(name,width=15,side="right",ellipsis = "")) %>% #create shorter names
  na.omit() #remove NAs

```
```{r data, echo=F}
head(df_long) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```


The distribution of ranks shows variation across all options with 'Configure remote...' looking to be lowest and 'Options to enroll...' looking to be the highest.


```{r plot, echo=F}

df_long %>%
  ggplot(aes(value, fill=name_s)) +
  geom_histogram(binwidth = 1) +
  geom_label(aes(label=name_s,y=3,x=4),fill="white")+
  facet_wrap(~name_s,ncol=1) +
  ggthemes::theme_tufte(base_family = "sans",base_size = 15) +
  theme(
    legend.position = "none",
    strip.text.x = element_blank()
  )  +
  scale_x_continuous(breaks = c(1,4,7)) +
  labs(y="Rank Count",x="Rank",caption = "1 is most important, 7 is least important") 

```

## Rank tests

With our rank data, we'll need to use a non-parametric approach to assess statistical significance of the ranks. Our data are an unreplicated block design (where we treat blocks as participants) so we can use the Friedman test and its an exact posthoc test. Below we see that the test is signficant so ranks differ between customization options. The effect size is small, but not miniscule. 

```{r mod, echo=F}

#friedman test
res.fried <- df_long %>%
  friedman_test(value ~ name_s | id)
res.fried %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

#effect size
df_long %>%
  friedman_effsize(value ~ name_s | id) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))


```
Now we need to conduct the posthoc test to see which options are statistically at a different rank. We use a pairwise Wilcoxon-Sign to see which options are significantly different from each other.


```{r posthoc, echo=F}

mod.pairwise <- df_long %>%
  arrange(id) %>% #order needs to be by ID
  pairwise_wilcox_test(value ~ name_s, p.adjust.method = "holm")

mod.pairwise %>%
  arrange(p) %>%
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

```







